Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
debugging ruleInduction

    ruleinduction(
      confidence = 0,
      control    = list(verbose = FALSE)
      )

@@

### Editing AR
```{r SR edit}
    mutate_at(
      c("support",
        "confidence", "lift"),
      funs(round(., 5))
    ) %>%
    filter(!`LHS Course ID`==`RHS Course ID`) %>%
    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
```

>>>>

    ruleInduction(
      confidence = 0,
      control    = list(verbose = FALSE)
      )

@@

### Editing SR
```{r SR edit}
    mutate_at(
      c("support",
        "confidence", "lift"),
      funs(round(., 5))
    ) %>%
    filter(!`LHS Course ID`==`RHS Course ID`) %>%
    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
```
